---
output: github_document
---

[![Travis build status](https://travis-ci.org/moodymudskipper/liblog.svg?branch=master)](https://travis-ci.org/moodymudskipper/liblog)
[![Codecov test coverage](https://codecov.io/gh/moodymudskipper/liblog/branch/master/graph/badge.svg)](https://codecov.io/gh/moodymudskipper/liblog?branch=master)


```{r, include = FALSE}
knitr::opts_chunk$set(
  eval=FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# liblog

This  package logs calls to loadNamespace, so one can track thei use of packages.

Install with:

``` r
remotes::install_github("moodymudskipper/liblog")
```

## Suggested use

Edit your R profile, (you can run `file.edit(file.path(R.home(), "etc", "RProfile.site"))`)
and add the following line at the end : 

```{r}
liblog::use_liblog()
```

It will display the following message each time you start R:

> Tracing function "loadNamespace" in package "base"
> to log loaded namespaces in 'C:/PROGRA~1/R/R-36~1.2/loadNamespace.log'

The actual path will change depending on your system.

If you'd rather do it silently, use `liblog::use_liblog(verbose = FALSE)` instead.

From there on, each time a package has its namespace loaded (not only attached!),
a new line will be added to the file mentionned in the message, you can get
this path by calling `getOption("liblog.path")` and you can choose another path
by adding a call to `options()`  before `use_liblog()` call in your RProfile 
so you'll have: 

```{r}
options(liblog.path = your_path)
liblog::use_liblog()
```

## Test it!

Apply the steps above, restart R (in RStudio : ctrl + shift + F10), then
see what's been logged already by calling : 

```{r}
file.edit(getOption("liblog.path"))
```

Duplicates are present because `loadNamespace()` is really called several times
on some packages.

More conveniently, you can call `liblog::get_liblog()`, which by default removes
duplicate records and ignores base and recommended packages.

## Is that it ?

For now it is, after I've used it for some time I think I'll implement some
visualization functions wrapped on `get_liblog()`. Maybe I'll also need some
options or utilisties to flush or archive the log, or warn about it getting too big,
but I need data first! (or feedback, wink wink => POST ISSUES AND HELP ME HELP YOU!).
